The Design Space of Network Mobility

### 2013-07-25 Compiled/chapter1/copyright.tex
first pass of references on chapter 1

%define \copyrightstatement command for easier use
\newcommand{\copyrightstatement}{
    \begin{textblock}{0.7}(0.08,0.9)    % tweak here: {box width}(leftposition, rightposition)
         \noindent
         \footnotesize
         P. Zave, J. Rexford, ``The Design Space of Network
         Mobility'', in H. Haddadi, O. Bonaventure (Eds.), \emph{Recent
         Advances in Networking}, (2013), pp. 5-45. Licensed under a
         creative commons license and available from \url{http://www.sigcomm.org}
    \end{textblock}
}

>>>>

%define \copyrightstatement command for easier use
\newcommand{\copyrightstatement}{
    \begin{textblock}{0.65}(0.17,0.9)    % tweak here: {box width}(hposition, vposition)
         \noindent
         \footnotesize
         P. Zave, J. Rexford, ``The Design Space of Network
         Mobility'', in H. Haddadi, O. Bonaventure (Eds.), \href{http://www.sigcomm.org}{\emph{Recent
         Advances in Networking}}, (2013), pp. xx-yy. Licensed under a
         \href{http://creativecommons.org/licenses/by-sa/3.0/}{CC-BY-SA} license. 
    \end{textblock}
}
